---
title: "B1"
author: "Terry Kwan"
date: "2022-11-04"
output: github_document
---

# Getting Started
Load the libraries for this assignment: 
```{r, message = F}
library(tidyverse)
library(datateachr)
library(testthat)
```

# Exercise 1 & 2: Make your function and document it
```{r}
#' @title convert_all_numericNA_to_median function
#' 
#' @details This function will convert all the NA in the numeric columns to the median value in that column.
#' 
#' @param data, the tibble to be converted
#' 
#' @return another tibble that does not have NA in numeric columns
#' 
convert_all_numericNA_to_median <- function(data) {
  data %>% 
    mutate(
      across(
        where(is.numeric), ~if_else(is.na(.x), median(.x, na.rm = T), as.numeric(.x))
      )
    )
}
```

# Exercise 3 examples
So basically here is a sample data with some NA values in the numeric columns, and the function will output another tribble that does not contain NA in the numeric columns.
```{r}
data <- tribble(
  ~name,            ~birth_weight,  ~birth_year, 
  "Luke Skywalker",  1.35      ,   1998        , 
  "C-3PO"         ,  NA        ,   2000        ,  
  "R2-D2"         ,  2.25      ,   NA        ,  
  "Darth Vader"   ,  2.70      ,   NA        ,  
)
convert_all_numericNA_to_median(data)
```

# Exercise 4 test
So basically here is a sample data with some NA values in the numeric columns, and the function will output another tribble that does not contain NA in the numeric columns.

### Test 1 (If there are NAs in the numeric columns, function will change those NAs to the median in the column)
```{r}
test_case_1_actual <- tribble(
  ~name,            ~birth_weight,  ~birth_year, 
  "Luke Skywalker",  1.35      ,   1998        , 
  "C-3PO"         ,  NA        ,   2000        ,  
  "R2-D2"         ,  2.25      ,   NA        ,  
  "Darth Vader"   ,  2.70      ,   NA        ,  
) 
test_case_1_expected <- tribble(
  ~name,            ~birth_weight,  ~birth_year, 
  "Luke Skywalker",  1.35      ,   1998        , 
  "C-3PO"         ,  2.25      ,   2000        ,  
  "R2-D2"         ,  2.25      ,   1999        ,  
  "Darth Vader"   ,  2.70      ,   1999        ,  
)
test_that("Test 1 - Happy Flow:", {
  expect_equal(convert_all_numericNA_to_median(test_case_1_actual), test_case_1_expected)
})
```

### Test 2 (If the orginal tribble does not contain any numeric NAs, the function will output the same original tribble. Note that the non-numeric columns will NOT be affected in any case)
```{r}
test_case_2_actual <- tribble(
  ~name,            ~birth_weight,  ~birth_year, 
  NA              ,  1.35      ,   1998        , 
  NA              ,  1.35      ,   2000        ,  
  "R2-D2"         ,  2.25      ,   2001        ,  
  "Darth Vader"   ,  2.70      ,   2002        ,  
) 
test_case_2_expected <- tribble(
  ~name,            ~birth_weight,  ~birth_year, 
  NA              ,  1.35      ,   1998        , 
  NA              ,  1.35      ,   2000        ,  
  "R2-D2"         ,  2.25      ,   2001        ,  
  "Darth Vader"   ,  2.70      ,   2002        ,  
) 
test_that("Test 2 - Happy Flow:", {
  expect_equal(convert_all_numericNA_to_median(test_case_2_actual), test_case_2_expected)
})
```

### Test 3 (If all numeric values are already NA, that means there is no median or the median is just simply NA)
```{r}
test_case_3_actual <- tribble(
  ~name,            ~birth_weight,  ~birth_year, 
  "Luke Skywalker",  NA      ,   2000        , 
  "C-3PO"         ,  NA      ,   NA        ,  
) 
test_case_3_expected <- tribble(
  ~name,            ~birth_weight,  ~birth_year, 
  "Luke Skywalker",  NA      ,   2000        , 
  "C-3PO"         ,  NA      ,   2000        ,  
) 
test_that("Test 1 - Happy Flow:", {
  expect_equal(convert_all_numericNA_to_median(test_case_3_actual), test_case_3_expected)
})
```